Poseidon Adventure

### 2019-05-22 docs/index.Rmd
add sardines examples

@@

>>>>

### An example workflow for a single species (in progress)

<a href="https://sgaichas.github.io/poseidon-dev/FullSardineTruthEx.html" target="_blank">Sardines in the CalCurrent, all true data, May 22, 2019</a>

<a href="https://sgaichas.github.io/poseidon-dev/CreateStockSynthesis.html" target="_blank">Sardines in the CalCurrent, input to SS functions, May 22, 2019</a>

@@

May 20-22: Fisheries, corrections to nums at age for Cal Current and decision to read in the catch.txt file for total catch in weight
